---
title: Assignment 4 - Trucks
author:
  - name: Troy Yang
    email: yang.tr@husky.neu.edu
    affiliation: Khoury
abstract: |
  This is my report for the truck factor assignment. The truck factor is not an original idea, but rather this is an application of the truck factor analysis on the R project. This RMD file can do this same analysis for other projects, it just needs to be pointed at a different dataset.
output: rticles::acm_article
---

```{r, echo=FALSE, warning=FALSE,message=FALSE}
library(dplyr)
library(rticles)
library(readr)
library(ggplot2)
setwd("C:/Users/bingb/Desktop/DS4900-HW/A4")
df <-read.csv("wch_rsource_master_only.csv.gz")
df %>%
  select(committer, committer.timestamp, hash, file.path) %>%
  rename(time = committer.timestamp, file = file.path) -> renamed

renamed %>% 
  filter( grepl(".scala$|\\.swift$|\\.js$|\\.cpp$|\\.h$|\\.java$|\\.c$|\\.php$|\\.groovy$|\\.sql$|\\.py$", file)) -> clean


files <- unique(clean$file)

clean %>% 
  group_by(file, committer) %>% 
  summarise(DL=n()) -> file_by_committer

clean %>% 
  group_by(file) %>% 
  summarise(AC=n()) -> num_committer_by_file

clean %>%
   group_by(file)  %>% 
   arrange(time, .by_group = TRUE) %>%
   summarize(first=first(committer)) -> first_committer

file_by_committer %>% 
  inner_join(first_committer, by = "file") %>% 
  inner_join(num_committer_by_file, by="file") %>%
  mutate(FA = committer == first) -> doa

doa %>%
  mutate(truck = 3.293+(1.098*FA) + (0.164*DL) - (0.321*log(1+AC))) -> doa

doa %>%
  group_by(file) %>%
  arrange(desc(truck), .by_group=T) %>%
  summarize(first = first(committer)) -> doa

num_files <- length(unique(doa$file))

doa %>% 
  group_by(first) %>%
  summarize(n=n()) %>%
  arrange(desc(n)) %>%
  mutate(num_files = num_files) %>%
  mutate(percent = n/num_files) -> doa

cs <- cumsum(doa$percent)
doa %>%
  mutate(cs = cs) %>%
  mutate(truck = cs < .5) -> doa

truck_factor = sum(doa$truck) + 1


```

# Introduction

The original data set has `r length(unique(df$hash))` unique commmits made on `r length(unique(df$file))` files by `r length(unique(df$committer))` committers. Upon removing files that are not relevant for this analysis, such as files that are not code, `r length(unique(clean$file))` files remain for analysis. Truck factor is determined by how many authors needs to be removed in order to have less than 50% of files be orphaned.

# Methods

R and R Studio were used to perform this analysis. Packages such as dplyr and readr were used to help perform the analysis, while rticles and ggplot were used for the presentation/delivery of this analysis. This analysis used the same formula as the original authors to determine degree of ownership on files. The formula is as follows DOA = 3.293 + 1.098 * FA + 0.164 * DL - 0.321 * ln(1 + AC ) where FA is first authorship, DL is number of deliveries and AC is the number of accepted changes. Once I had calculated the needed parameters and could determine file ownership, I looked to see how many committers needed to be eliminated to have half the files be authorless.


# Results

For this project, the truck factor was found to be `r truck_factor`. As the follow visualization will show, 'ripley' had an overwhelming amount of files (`r doa[doa$first == 'ripley',]$n`) out of all the files in the project (`r doa[doa$first == 'ripley',]$num_files`) that were deemed to be theirs. One committer owning such a large proportion of the code files in the repository explains why the truck factor was so low.

```{r, echo=FALSE, warning=FALSE,message=FALSE}

p<-ggplot(data=doa[doa$n > 20,], aes(x=first, y=n)) +geom_bar(stat="identity", fill="steelblue")+
    geom_text(aes(label=n), vjust=-1, color="black", size=3)+  theme_minimal()  +
  ggtitle("Number of Files owned by Committer")
p
 
```





